Enzo: An Adaptive Mesh Refinement Code for Astrophysics

### 2013-06-11 overview.tex
Added comoving to E and p

The total fluid energy density $E$ is given by
\begin{equation}
E =  e + \frac{\rho v^2}{2}  + \frac{B^2}{2a}
        \label{eq:total_energy_def},
\end{equation}
where $e$ is the comoving thermal energy density, the total
isotropic pressure $p^*$ is given by
\begin{equation}
p^* = p + \frac{B^2}{2a},
\end{equation}
and $p$ is the thermal pressure.  The equations are closed by an
equation of state and Poisson's equation (in the Newtonian limit) for
the gravitational potential $\phi$:
%
\begin{eqnarray}
%
  e &=& \frac{p}{(\gamma - 1) \rho},
  \label{eq:eq_of_state} \\
%
  \nabla^2 \phi &=& 4 \pi G \left( \rho_{\rm total} - \rho_0 \right)
%                   + 3 p_{total}/c^2) - \Lambda. 
  \label{eq:potential}
\end{eqnarray}
%
The equation of state is shown here for an ideal gas with a ratio of
specific heats $\gamma$.  The gravitational potential $\phi$ is
sourced by the total mass density contrast, where $\rho_{\rm total} =
\rho_{\rm gas} + \rho_{\rm dm} + \rho_{\rm stars}$ and $\rho_0$ is the
mean density.  Although we write the equations including both magnetic
field terms and comoving coordinates, the code is frequently used both
in the purely hydrodynamic limit ($\vecB = 0$, referred to as HD
below) and without cosmological expansion ($a = 1$, $\dot{a} = 0$).

>>>>

The comoving total fluid energy density $E$ is given by
\begin{equation}
E =  e + \frac{\rho v^2}{2}  + \frac{B^2}{2a}
        \label{eq:total_energy_def},
\end{equation}
where $e$ is the comoving thermal energy density, the total comoving
isotropic pressure $p^*$ is given by
\begin{equation}
p^* = p + \frac{B^2}{2a},
\end{equation}
and $p$ is the thermal pressure.  The equations are closed by an
equation of state and Poisson's equation (in the Newtonian limit) for
the gravitational potential $\phi$:
%
\begin{eqnarray}
%
  e &=& \frac{p}{(\gamma - 1) \rho},
  \label{eq:eq_of_state} \\
%
  \nabla^2 \phi &=& 4 \pi G \left( \rho_{\rm total} - \rho_0 \right)
%                   + 3 p_{total}/c^2) - \Lambda. 
  \label{eq:potential}
\end{eqnarray}
%
The equation of state is shown here for an ideal gas with a ratio of
specific heats $\gamma$.  The gravitational potential $\phi$ is
sourced by the total mass density contrast, where $\rho_{\rm total} =
\rho_{\rm gas} + \rho_{\rm dm} + \rho_{\rm stars}$ and $\rho_0$ is the
mean density.  Although we write the equations including both magnetic
field terms and comoving coordinates, the code is frequently used both
in the purely hydrodynamic limit ($\vecB = 0$, referred to as HD
below) and without cosmological expansion ($a = 1$, $\dot{a} = 0$).
